An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-21 draft.tex
PNGs to Vector Pdfs

We have mentioned several advantages of a cloud-native application for running
multi-population based algorithms, but there are in our experience several
practical issues of this approach. In general, cloud platforms have free-tiers
for their services, and many offer academic discounts to students. But once we
pass to the pay-as-you-go tier, computing resources need to be managed.  First,
in many cases, there is a credit-card need to guarantee the payment of the
resources consumed and someone responsible for assigning quotas and, more
importantly, special keys for using the cloud's API.  If these keys are
compromised or shared by their holders,  additional costs or administrative
procedures are in order. For those cases when a prototype platform is needed,
for instance, students developing a new algorithm variant or experimenting with
a published work, a container-based platform can be more practical.

\subsection{Containers} 
\label{edm}

\subsection{Docker compose} 
\label{edm}

>>>>

We have mentioned several advantages of a cloud-native application for running
multi-population based algorithms, but there are in our experience several
practical issues of this approach. In general, cloud platforms have free-tiers
for their services, and many offer academic discounts to students. But once we
pass to the pay-as-you-go tier, computing resources need to be managed.  First,
in many cases, there is a credit-card need to guarantee the payment of the
resources consumed and someone responsible for assigning quotas and, more
importantly, special keys for using the cloud's API.  If these keys are
compromised or shared by their holders,  additional costs or administrative
procedures are in order. For those cases when a prototype platform is needed,
for instance, students developing a new algorithm variant or experimenting with
a published work, a container-based platform can be more practical.Container
technology enables researchers the local deployment of all the infrastructure
needed to run the experiments. Later, if needed, the same deployment could be
deployed to the cloud.

In this section, we propose a design of a reactive container-based application
for executing multi-population based optimization experiments.  For the design,
we followed the design patterns highlighted in the previous section, and again
we can go back to Figure \ref{fig:kafkEO} and use it as a guide for explaining
the main components and their interactions. But first, we give a brief
description of the technology we used.

\subsection{Containers} 
\label{containers}
% TO DO

\subsection{Docker compose} 
\label{edm}
% TO DO
